---
title       : Data Product Pitch
subtitle    : MPG shiny App
author      : 
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## mtcars: MPG and Cylinders

My shiny app is a calculator based on the relationship between the number of cylinders and mpg.

```{r, echo=FALSE}
library(datasets)
library(ggplot2)
ggplot(mtcars, aes(factor(cyl), mpg)) + geom_boxplot(aes(fill = factor(cyl)))
```

--- .class #id 

## The input
The app takes a single input: the number of cylinders.  You select either 4, 6, or 8.

--- .class #id 

## The calculation
The prediction is based upon a linear regression with a single variable
```{r}
library(datasets)
dat <- mtcars
fit <- lm(mpg ~ cyl, data = dat)
fit
```

--- .class #id 

## The prediction
After selecting the number of cylinders, the output is the regression function evaluated using the number of cylinders you indicate, for example, 6:
```{r}
as.numeric(predict(fit,data.frame(cyl=6))) 
```





